---
title: "MI Paper Plots"
author: "Kylie Getz and Kristin Linn"
date: "6/28/2022"
output: pdf_document
---

Results using 1000 simulations, 10 MI
trueTreatment approx -0.69, trueEcog appox 0.4

os1 <- coxph(Surv(cmonth, dead) ~ treat + genderf +  
reth_black + reth_hisp + reth_oth + practypec + b.ecogvalue + smokey +  dgradeh + surgery + site_ureter + site_renal + site_urethra + age + var1 + var2, data=sdat.c, x=T)


```{r echo=F, include=F}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(grid)
library(xtable)
library(kableExtra)
library(dplyr)
library(reshape2)

mi_plots = FALSE

rootdir = "~/Box Sync/Mentoring/Students/Getz_Kylie/results"
#rootdir = "~/Box/Mentoring/Students/Getz_Kylie/results"
regDir = file.path (rootdir, "2022_06_28/final_results")
simpDir = file.path (rootdir, "2022_06_28/final_simple")
ldDir = file.path (rootdir, "2022_06_28/final_lowDim")

getDfs <- function (mdm, pc, fdir=regDir, aedir=regDir){
  # Oracle, CC, MICE, and RF
  avgName = paste0 ("Avgs_", mdm, "_", pc, ".csv")
  percName = paste0 ("Percentiles_", mdm, "_", pc, ".csv")
  avgDf = read.csv (file.path (fdir, avgName))
  percDf = read.csv (file.path (fdir, percName))
  percDf$X = NULL
  # AE
  avgName = paste0 ("AE", avgName)  
  percName = paste0 ("AE", percName)  
  aeAvg =  read.csv (file.path (aedir, avgName))
  colnames (aeAvg) = c ("X", "biasAE", "seAE", "coverageAE", "mseAE")
  aeAvg$X = avgDf$X
  aePerc =  read.csv (file.path (fdir, percName))
  aePerc$X = NULL
  colnames(aePerc)[1] = 'treat'
  aePerc$method = 'DAE'
  avgDf = left_join (avgDf, aeAvg, by='X')
  percDf = rbind (percDf, aePerc)
  percDf$prop = pc
  percDf$mech = mdm
  return (list ('avg'=avgDf, 'perc'=percDf))
}
```

# Full outcome model, original DAE layers
```{r echo=F, include=F}
MCAR10 = getDfs ('MCAR', 10)
MCAR30 = getDfs ('MCAR', 30)
MCAR50 = getDfs ('MCAR', 50)
MCAR = rbind (MCAR10$perc, MCAR30$perc, MCAR50$perc)

MAR10 = getDfs ('MAR', 10)
MAR30 = getDfs ('MAR', 30)
MAR50 = getDfs ('MAR', 50)
MAR = rbind (MAR10$perc, MAR30$perc, MAR50$perc)

MNAR10a = getDfs ('MNAR1', 10)
MNAR30a = getDfs ('MNAR1', 30)
MNAR50a = getDfs ('MNAR1', 50)
MNAR1 = rbind (MNAR10a$perc, MNAR30a$perc, MNAR50a$perc)

MNAR10b = getDfs ('MNAR2', 10)
MNAR30b = getDfs ('MNAR2', 30)
MNAR50b = getDfs ('MNAR2', 50)
MNAR2 = rbind (MNAR10b$perc, MNAR30b$perc, MNAR50b$perc)

allData = rbind (MCAR, MAR, MNAR1, MNAR2)
```

```{r echo=F, include=F}

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotOne <- function (data, mdm, variable, ylimit=NULL){
  varnames = names (data)
  keep = varnames[which (varnames==variable)]
  data$mech = factor (data$mech)
  data$method = factor (data$method, levels=c("ORACLE", "CC", "MICE", "RF", "DAE"))
  data = dplyr::select (data, all_of(keep), mech, prop, method)
  colnames (data)[1] = 'y'
  dat = dplyr::filter (data, mech==mdm)
  datOracle = dplyr::filter (dat, method=='ORACLE' & prop==10)
  dat = dplyr::filter (dat, !(method=='ORACLE'))
  datOracle$prop = ""
  fdat = rbind (datOracle, dat)
  gg = ggplot(fdat, aes(x=method, y=y, fill=method)) + 
    ylab("Estimate - True") +
    xlab("") +
    ggtitle(mdm) + 
    geom_boxplot() + 
#    geom_errorbar(aes(ymax = Upper, ymin = Lower), position = "dodge",size = 1.5) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
#    geom_point(shape=16,colour="black",size=2) +
#    facet_grid(cols=vars(prop), scales = "free_x", space="free_x", switch="both") +
    facet_grid(cols=vars(prop), scales = "free_x", space="free", switch="both") +
    theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y = element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1, size=8),
         panel.background = element_rect(fill = 'white', colour = 'white')) +
    scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE")) + 
    theme(legend.position = 'none') +
    scale_fill_manual(values=mycols)
    if (!is.null (ylimit)){
      gg = gg + coord_cartesian(ylim=ylimit)
    }
  return (gg)
}


percPlot = function (data, variable, y=NULL){
  mcar = plotOne (data, mdm='MCAR', variable, y)
  mar = plotOne (data, mdm='MAR', variable, y)
  mnar1 = plotOne (data, mdm='MNAR1', variable, y)
  mnar2 = plotOne (data, mdm='MNAR2', variable, y)
  op = grid.arrange(mcar, mar, mnar1, mnar2, nrow = 2)
  return (op)
}

```

\newpage

## treat

```{r echo=F}
percPlot(allData, 'treat')
```

\newpage

## genderf

```{r echo=F}
percPlot(allData, 'genderf')
```

\newpage

## reth_black

```{r echo=F}
percPlot(allData, 'reth_black')
```

\newpage

## reth_hisp

```{r echo=F}
percPlot(allData, 'reth_hisp')
```

\newpage

## reth_oth

```{r echo=F}
percPlot(allData, 'reth_oth')
```

\newpage

## practypec

```{r echo=F}
percPlot(allData, 'practypec')
```

\newpage

## b.ecogvalue

```{r echo=F}
percPlot(allData, 'b.ecogvalue')
```

\newpage

## smokey

```{r echo=F}
percPlot(allData, 'smokey')
```

\newpage

## dgradeh

```{r echo=F}
percPlot(allData, 'dgradeh')
```

\newpage

## surgery

```{r echo=F}
percPlot(allData, 'surgery')
```

\newpage

## site_ureter

```{r echo=F}
percPlot(allData, 'site_ureter')
```

\newpage

## site_renal

```{r echo=F}
percPlot(allData, 'site_renal')
```

\newpage

## site_urethra

```{r echo=F}
percPlot(allData, 'site_urethra')
```

\newpage

## age

```{r echo=F}
percPlot(allData, 'age')
```

\newpage

## var1

```{r echo=F}
percPlot(allData, 'var1')
```

\newpage

## var2
```{r echo=F}
percPlot(allData, 'var2')
```

## All Figures
```{r echo=F}
vars = names (allData)[1:16]
if (mi_plots){
  for (i in 1:length (vars)){
    pdf (paste0 ('~/Desktop/mi_plots/regular_', vars[i], '.pdf'))
    percPlot(allData, vars[i])
    dev.off()
  }
}

# With fixed y axis
pdf (paste0 ('~/Desktop/plotAllECOG.pdf'), width=6, height=6, pointsize=1)
percPlot(allData, 'b.ecogvalue', y=c(-0.3,0.2))
dev.off()
pdf (paste0 ('~/Desktop/plotAllTreat.pdf'), width=6, height=6, pointsize=1)
percPlot(allData, 'treat', y=c(-0.5,0.5))
dev.off()

```



# Simple outcome model, original DAE layers
```{r echo=F, include=F}
MCAR10 = getDfs ('MCAR', 10, simpDir, simpDir)
MCAR30 = getDfs ('MCAR', 30, simpDir, simpDir)
MCAR50 = getDfs ('MCAR', 50, simpDir, simpDir)
MCAR = rbind (MCAR10$perc, MCAR30$perc, MCAR50$perc)

MAR10 = getDfs ('MAR', 10, simpDir, simpDir)
MAR30 = getDfs ('MAR', 30, simpDir, simpDir)
MAR50 = getDfs ('MAR', 50, simpDir, simpDir)
MAR = rbind (MAR10$perc, MAR30$perc, MAR50$perc)

MNAR10a = getDfs ('MNAR1', 10, simpDir, simpDir)
MNAR30a = getDfs ('MNAR1', 30, simpDir, simpDir)
MNAR50a = getDfs ('MNAR1', 50, simpDir, simpDir)
MNAR1 = rbind (MNAR10a$perc, MNAR30a$perc, MNAR50a$perc)

MNAR10b = getDfs ('MNAR2', 10, simpDir, simpDir)
MNAR30b = getDfs ('MNAR2', 30, simpDir, simpDir)
MNAR50b = getDfs ('MNAR2', 50, simpDir, simpDir)
MNAR2 = rbind (MNAR10b$perc, MNAR30b$perc, MNAR50b$perc)

allData = rbind (MCAR, MAR, MNAR1, MNAR2)
```

```{r echo=F, include=F}

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotOne <- function (data, mdm, variable){
  varnames = names (data)
  keep = varnames[which (varnames==variable)]
  data$mech = factor (data$mech)
  data$method = factor (data$method, levels=c("ORACLE", "CC", "MICE", "RF", "DAE"))
  data = dplyr::select (data, all_of(keep), mech, prop, method)
  colnames (data)[1] = 'y'
  dat = dplyr::filter (data, mech==mdm)
  datOracle = dplyr::filter (dat, method=='ORACLE' & prop==10)
  dat = dplyr::filter (dat, !(method=='ORACLE'))
  datOracle$prop = ""
  fdat = rbind (datOracle, dat)
  gg = ggplot(fdat, aes(x=method, y=y, fill=method)) + 
    ylab("Estimate - True") +
    xlab("") +
    ggtitle(mdm) + 
    geom_boxplot() + 
#    geom_errorbar(aes(ymax = Upper, ymin = Lower), position = "dodge",size = 1.5) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
#    geom_point(shape=16,colour="black",size=2) +
#    facet_grid(cols=vars(prop), scales = "free_x", space="free_x", switch="both") +
    facet_grid(cols=vars(prop), scales = "free_x", space="free", switch="both") +
    theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y = element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1, size=8),
         panel.background = element_rect(fill = 'white', colour = 'white')) +
    scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE")) + 
    theme(legend.position = 'none') +
    scale_fill_manual(values=mycols)
  return (gg)
}


percPlot = function (data, variable){
  mcar = plotOne (data, mdm='MCAR', variable)
  mar = plotOne (data, mdm='MAR', variable)
  mnar1 = plotOne (data, mdm='MNAR1', variable)
  mnar2 = plotOne (data, mdm='MNAR2', variable)
  op = grid.arrange(mcar, mar, mnar1, mnar2, nrow = 2)
  return (op)
}

```

\newpage

## treat

```{r echo=F}
percPlot(allData, 'treat')
```

\newpage

## b.ecogvalue

```{r echo=F}
percPlot(allData, 'b.ecogvalue')
```

## All Figures
```{r echo=F}
if (mi_plots){
pdf (paste0 ('~/Desktop/mi_plots/simple_treat.pdf'))
percPlot(allData, 'treat')
dev.off()

pdf (paste0 ('~/Desktop/mi_plots/simple_b.ecogvalue.pdf'))
percPlot(allData, 'b.ecogvalue')
dev.off()
}
```


# Full outcome model, fewer DAE layers
```{r echo=F, include=F}
MCAR10 = getDfs ('MCAR', 10, regDir, ldDir)
MCAR30 = getDfs ('MCAR', 30, regDir, ldDir)
MCAR50 = getDfs ('MCAR', 50, regDir, ldDir)
MCAR = rbind (MCAR10$perc, MCAR30$perc, MCAR50$perc)

MAR10 = getDfs ('MAR', 10, regDir, ldDir)
MAR30 = getDfs ('MAR', 30, regDir, ldDir)
MAR50 = getDfs ('MAR', 50, regDir, ldDir)
MAR = rbind (MAR10$perc, MAR30$perc, MAR50$perc)

MNAR10a = getDfs ('MNAR1', 10, regDir, ldDir)
MNAR30a = getDfs ('MNAR1', 30, regDir, ldDir)
MNAR50a = getDfs ('MNAR1', 50, regDir, ldDir)
MNAR1 = rbind (MNAR10a$perc, MNAR30a$perc, MNAR50a$perc)

MNAR10b = getDfs ('MNAR2', 10, regDir, ldDir)
MNAR30b = getDfs ('MNAR2', 30, regDir, ldDir)
MNAR50b = getDfs ('MNAR2', 50, regDir, ldDir)
MNAR2 = rbind (MNAR10b$perc, MNAR30b$perc, MNAR50b$perc)

allData = rbind (MCAR, MAR, MNAR1, MNAR2)
```

```{r echo=F, include=F}

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotOne <- function (data, mdm, variable, ylimit=NULL){
  varnames = names (data)
  keep = varnames[which (varnames==variable)]
  data$mech = factor (data$mech)
  data$method = factor (data$method, levels=c("ORACLE", "CC", "MICE", "RF", "DAE"))
  data = dplyr::select (data, all_of(keep), mech, prop, method)
  colnames (data)[1] = 'y'
  dat = dplyr::filter (data, mech==mdm)
  datOracle = dplyr::filter (dat, method=='ORACLE' & prop==10)
  dat = dplyr::filter (dat, !(method=='ORACLE'))
  datOracle$prop = ""
  fdat = rbind (datOracle, dat)
  gg = ggplot(fdat, aes(x=method, y=y, fill=method)) + 
    ylab("Estimate - True") +
    xlab("") +
    ggtitle(mdm) + 
    geom_boxplot() + 
#    geom_errorbar(aes(ymax = Upper, ymin = Lower), position = "dodge",size = 1.5) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
#    geom_point(shape=16,colour="black",size=2) +
#    facet_grid(cols=vars(prop), scales = "free_x", space="free_x", switch="both") +
    facet_grid(cols=vars(prop), scales = "free_x", space="free", switch="both") +
    theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y = element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1, size=8),
         panel.background = element_rect(fill = 'white', colour = 'white')) +
    scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE")) + 
    theme(legend.position = 'none') +
    scale_fill_manual(values=mycols)
    if (!is.null (ylimit)){
      gg = gg + coord_cartesian(ylim=ylimit)
    }
  return (gg)
}


percPlot = function (data, variable, y=NULL){
  mcar = plotOne (data, mdm='MCAR', variable, y)
  mar = plotOne (data, mdm='MAR', variable, y)
  mnar1 = plotOne (data, mdm='MNAR1', variable, y)
  mnar2 = plotOne (data, mdm='MNAR2', variable, y)
  op = grid.arrange(mcar, mar, mnar1, mnar2, nrow = 2)
  return (op)
}

```

\newpage

## treat

```{r echo=F}
percPlot(allData, 'treat')
```

\newpage

## genderf

```{r echo=F}
percPlot(allData, 'genderf')
```

\newpage

## reth_black

```{r echo=F}
percPlot(allData, 'reth_black')
```

\newpage

## reth_hisp

```{r echo=F}
percPlot(allData, 'reth_hisp')
```

\newpage

## reth_oth

```{r echo=F}
percPlot(allData, 'reth_oth')
```

\newpage

## practypec

```{r echo=F}
percPlot(allData, 'practypec')
```

\newpage

## b.ecogvalue

```{r echo=F}
percPlot(allData, 'b.ecogvalue')
```

\newpage

## smokey

```{r echo=F}
percPlot(allData, 'smokey')
```

\newpage

## dgradeh

```{r echo=F}
percPlot(allData, 'dgradeh')
```

\newpage

## surgery

```{r echo=F}
percPlot(allData, 'surgery')
```

\newpage

## site_ureter

```{r echo=F}
percPlot(allData, 'site_ureter')
```

\newpage

## site_renal

```{r echo=F}
percPlot(allData, 'site_renal')
```

\newpage

## site_urethra

```{r echo=F}
percPlot(allData, 'site_urethra')
```

\newpage

## age

```{r echo=F}
percPlot(allData, 'age')
```

\newpage

## var1

```{r echo=F}
percPlot(allData, 'var1')
```

\newpage

## var2
```{r echo=F}
percPlot(allData, 'var2')
```

## All Figures
```{r echo=F}
vars = names (allData)[1:16]
if (mi_plots){
  for (i in 1:length (vars)){
    pdf (paste0 ('~/Desktop/mi_plots/lowDim_', vars[i], '.pdf'))
    percPlot(allData, vars[i])
    dev.off()
  }
}

# With fixed y axis
pdf (paste0 ('~/Desktop/plotAllECOG_lowDim.pdf'), width=6, height=6, pointsize=1)
percPlot(allData, 'b.ecogvalue', y=c(-0.3,0.2))
dev.off()
pdf (paste0 ('~/Desktop/plotAllTreat_lowDim.pdf'), width=6, height=6, pointsize=1)
percPlot(allData, 'treat', y=c(-0.5,0.5))
dev.off()
```
