---
title: "MIPaperFigures"
author: "Kylie Getz and Kristin Linn"
date: "5/7/2022"
output: pdf_document
---

Results using 1000 simulations, 10 MI
trueTreatment approx -0.69, trueEcog appox 0.4

os1 <- coxph(Surv(cmonth, dead) ~ treat + genderf +  
reth_black + reth_hisp + reth_oth + practypec + b.ecogvalue + smokey +  dgradeh + surgery + site_ureter + site_renal + site_urethra + age + var1 + var2, data=sdat.c, x=T)


```{r echo=F, include=F}
library(ggplot2)
require(gridExtra)
library(grid)
library(xtable)
library(kableExtra)

rootdir = "~/Box Sync/Mentoring/Students/Getz_Kylie/results"
fdir = file.path (rootdir, "2022_05_15")
MCAR10 <- read.csv(file.path (fdir, "MCAR10Avg10TreeV2.csv"),row.names = 1)
MCAR30 <- read.csv(file.path (fdir,"MCAR30Avg10TreeV2.csv"),row.names = 1)
MCAR50 <- read.csv(file.path (fdir,"MCAR50Avg10TreeV2.csv"),row.names = 1)
MAR10 <- read.csv(file.path (fdir,"MAR10Avg10TreeV2.csv"),row.names = 1)
MAR30 <- read.csv(file.path (fdir,"MAR30Avg10TreeV2.csv"),row.names = 1)
MAR50 <- read.csv(file.path (fdir,"MAR50Avg10TreeV2.csv"),row.names = 1)
MNAR10a <- read.csv(file.path (fdir,"MNAR10aAvg10TreeV2.csv"),row.names = 1)
MNAR30a <- read.csv(file.path (fdir,"MNAR30aAvg10TreeV2.csv"),row.names = 1)
MNAR50a <- read.csv(file.path (fdir,"MNAR50aAvg10TreeV2.csv"),row.names = 1)
MNAR10b <- read.csv(file.path (fdir,"MNAR10bAvg10TreeV2.csv"),row.names = 1)
MNAR30b <- read.csv(file.path (fdir,"MNAR30bAvg10TreeV2.csv"),row.names = 1)
MNAR50b <- read.csv(file.path (fdir,"MNAR50bAvg10TreeV2.csv"),row.names = 1)

MCAR10AE <- read.csv(file.path (fdir,"AEresult10TreeMCAR10.csv"),row.names = 1)
MCAR30AE <- read.csv(file.path (fdir,"AEresult10TreeMCAR30.csv"),row.names = 1)
MCAR50AE <- read.csv(file.path (fdir,"AEresult10TreeMCAR50.csv"),row.names = 1)
MAR10AE<- read.csv(file.path (fdir,"AEresult10TreeMAR10.csv"),row.names = 1)
MAR30AE <- read.csv(file.path (fdir,"AEresult10TreeMAR30.csv"),row.names = 1)
MAR50AE <- read.csv(file.path (fdir,"AEresult10TreeMAR50.csv"),row.names = 1)
MNAR10aAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR110.csv"),row.names = 1)
MNAR30aAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR130.csv"),row.names = 1)
MNAR50aAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR150.csv"),row.names = 1)
MNAR10bAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR210.csv"),row.names = 1)
MNAR30bAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR230.csv"),row.names = 1)
MNAR50bAE <- read.csv(file.path (fdir,"AEresult10TreeMNAR250.csv"),row.names = 1)

MCAR10Full <- cbind(MCAR10,MCAR10AE)
MCAR30Full <- cbind(MCAR30,MCAR30AE)
MCAR50Full <- cbind(MCAR50,MCAR50AE)
MAR10Full <- cbind(MAR10,MAR10AE)
MAR30Full <- cbind(MAR30,MAR30AE)
MAR50Full <- cbind(MAR50,MAR50AE)
MNAR10aFull<- cbind(MNAR10a,MNAR10aAE)
MNAR30aFull<- cbind(MNAR30a,MNAR30aAE)
MNAR50aFull <- cbind(MNAR50a,MNAR50aAE)
MNAR10bFull<- cbind(MNAR10b,MNAR10bAE)
MNAR30bFull<- cbind(MNAR30b,MNAR30bAE)
MNAR50bFull <- cbind(MNAR50b,MNAR50bAE)

MCAR10AEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMCAR10.csv"),row.names = 1)
MCAR30AEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMCAR30.csv"),row.names = 1)
MCAR50AEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMCAR50.csv"),row.names = 1)
MAR10AEPerc<- read.csv(file.path (fdir,"AEpercentile10TreeMAR10.csv"),row.names = 1)
MAR30AEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMAR30.csv"),row.names = 1)
MAR50AEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMAR50.csv"),row.names = 1)
MNAR10aAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR110.csv"),row.names = 1)
MNAR30aAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR130.csv"),row.names = 1)
MNAR50aAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR150.csv"),row.names = 1)
MNAR10bAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR210.csv"),row.names = 1)
MNAR30bAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR230.csv"),row.names = 1)
MNAR50bAEPerc <- read.csv(file.path (fdir,"AEpercentile10TreeMNAR250.csv"),row.names = 1)

AETreatPerc <- rbind(cbind(MCAR10AEPerc[,1],MCAR30AEPerc[,1],MCAR50AEPerc[,1]),cbind(MAR10AEPerc[,1],MAR30AEPerc[,1],MAR50AEPerc[,1]),cbind(MNAR10aAEPerc[,1],MNAR30aAEPerc[,1],MNAR50aAEPerc[,1]),cbind(MNAR10bAEPerc[,1],MNAR30bAEPerc[,1],MNAR50bAEPerc[,1]))

PercTreatMCAR <- read.csv(file.path (fdir,"PercentileTreatMCAR10TreeV2.csv"),row.names=1 )
colnames(PercTreatMCAR)  <- c("10","30","50")
AErow <- cbind(MCAR10AEPerc[,1],MCAR30AEPerc[,1],MCAR50AEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercTreatMCAR <- rbind(PercTreatMCAR,AErow)

PercEcogMCAR <- read.csv(file.path (fdir,"PercentileEcogMCAR10TreeV2.csv"),row.names=1 )
colnames(PercEcogMCAR)  <- c("10","30","50")
AErow <- cbind(MCAR10AEPerc[,2],MCAR30AEPerc[,2],MCAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercEcogMCAR <- rbind(PercEcogMCAR,AErow)

PercVar1MCAR <- read.csv(file.path (fdir,"PercentileVar1MCAR10TreeV2.csv"),row.names=1 )
colnames(PercVar1MCAR)  <- c("10","30","50")
AErow <- cbind(MCAR10AEPerc[,2],MCAR30AEPerc[,2],MCAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar1MCAR <- rbind(PercVar1MCAR,AErow)

PercVar2MCAR <- read.csv(file.path (fdir,"PercentileVar2MCAR10TreeV2.csv"),row.names=1 )
colnames(PercVar2MCAR)  <- c("10","30","50")
AErow <- cbind(MCAR10AEPerc[,2],MCAR30AEPerc[,2],MCAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar2MCAR <- rbind(PercVar2MCAR,AErow)

PercTreatMAR <- read.csv(file.path (fdir,"PercentileTreatMAR10TreeV2.csv"),row.names=1 )
colnames(PercTreatMAR)  <- c("10","30","50")
AErow <- cbind(MAR10AEPerc[,1],MAR30AEPerc[,1],MAR50AEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercTreatMAR <- rbind(PercTreatMAR,AErow)

PercEcogMAR <- read.csv(file.path (fdir,"PercentileEcogMAR10TreeV2.csv"),row.names=1 )
colnames(PercEcogMAR)  <- c("10","30","50")
AErow <- cbind(MAR10AEPerc[,2],MAR30AEPerc[,2],MAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercEcogMAR <- rbind(PercEcogMAR,AErow)

PercVar1MAR <- read.csv(file.path (fdir,"PercentileVar1MAR10TreeV2.csv"),row.names=1 )
colnames(PercVar1MAR)  <- c("10","30","50")
AErow <- cbind(MAR10AEPerc[,2],MAR30AEPerc[,2],MAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar1MAR <- rbind(PercVar1MAR,AErow)

PercVar2MAR <- read.csv(file.path (fdir,"PercentileVar2MAR10TreeV2.csv"),row.names=1 )
colnames(PercVar2MAR)  <- c("10","30","50")
AErow <- cbind(MAR10AEPerc[,2],MAR30AEPerc[,2],MAR50AEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar2MAR <- rbind(PercVar2MAR,AErow)

PercTreatMNAR1 <- read.csv(file.path (fdir,"PercentileTreatMNAR10aTreeV2.csv"),row.names=1 )
colnames(PercTreatMNAR1)  <- c("10","30","50")
AErow <- cbind(MNAR10aAEPerc[,1],MNAR30aAEPerc[,1],MNAR50aAEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercTreatMNAR1 <- rbind(PercTreatMNAR1,AErow)

PercEcogMNAR1 <- read.csv(file.path (fdir,"PercentileEcogMNAR10aTreeV2.csv"),row.names=1 )
colnames(PercEcogMNAR1)  <- c("10","30","50")
AErow <- cbind(MNAR10aAEPerc[,2],MNAR30aAEPerc[,2],MNAR50aAEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercEcogMNAR1 <- rbind(PercEcogMNAR1,AErow)

PercVar1MNAR1 <- read.csv(file.path (fdir,"PercentileVar1MNAR10aTreeV2.csv"),row.names=1 )
colnames(PercVar1MNAR1)  <- c("10","30","50")
AErow <- cbind(MNAR10aAEPerc[,2],MNAR30aAEPerc[,2],MNAR50aAEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar1MNAR1 <- rbind(PercVar1MNAR1,AErow)

PercVar2MNAR1 <- read.csv(file.path (fdir,"PercentileVar2MNAR10aTreeV2.csv"),row.names=1 )
colnames(PercVar2MNAR1)  <- c("10","30","50")
AErow <- cbind(MNAR10aAEPerc[,2],MNAR30aAEPerc[,2],MNAR50aAEPerc[,2])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar2MNAR1 <- rbind(PercVar2MNAR1,AErow)

PercTreatMNAR2 <- read.csv(file.path (fdir,"PercentileTreatMNAR10bTreeV2.csv"),row.names=1 )
colnames(PercTreatMNAR2)  <- c("10","30","50")
AErow <- cbind(MNAR10bAEPerc[,1],MNAR30bAEPerc[,1],MNAR50bAEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercTreatMNAR2 <- rbind(PercTreatMNAR2,AErow)

PercEcogMNAR2 <- read.csv(file.path (fdir,"PercentileEcogMNAR10bTreeV2.csv"),row.names=1 )
colnames(PercEcogMNAR2)  <- c("10","30","50")
AErow <- cbind(MNAR10bAEPerc[,1],MNAR30bAEPerc[,1],MNAR50bAEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercEcogMNAR2 <- rbind(PercEcogMNAR2,AErow)

PercVar1MNAR2 <- read.csv(file.path (fdir,"PercentileVar1MNAR10bTreeV2.csv"),row.names=1 )
colnames(PercVar1MNAR2)  <- c("10","30","50")
AErow <- cbind(MNAR10bAEPerc[,1],MNAR30bAEPerc[,1],MNAR50bAEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar1MNAR2 <- rbind(PercVar1MNAR2,AErow)

PercVar2MNAR2 <- read.csv(file.path (fdir,"PercentileVar2MNAR10bTreeV2.csv"),row.names=1 )
colnames(PercVar2MNAR2)  <- c("10","30","50")
AErow <- cbind(MNAR10bAEPerc[,1],MNAR30bAEPerc[,1],MNAR50bAEPerc[,1])
colnames(AErow) <- c("10","30","50")
rownames(AErow) <- c("AELower","AEUpper")
PercVar2MNAR2 <- rbind(PercVar2MNAR2,AErow)
```

```{r echo=F, include=F}
TreatInds = c (1,5,9,13)
EcogInds = c (2,6,10,14)
Var1Inds = c (3,7,11,15)
Var2Inds = c (4,8,12,16)
```

```{r echo=F, include=F}
# Table 1: Treat Bias and MSE
tab1MCAR10 <-t(MCAR10[c(1,4),TreatInds])
tab1MCAR30 <- t(MCAR30[c(1,4),TreatInds])
tab1MCAR50 <- t(MCAR50[c(1,4),TreatInds])
tab1MCAR <- cbind(tab1MCAR10[,1],tab1MCAR30[,1],tab1MCAR50[,1],tab1MCAR10[,2],tab1MCAR30[,2],tab1MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab1MCAR <- rbind(prop,tab1MCAR)

AEBiasMSE <- cbind(t(MCAR10AE)[1,1],t(MCAR30AE)[1,1],t(MCAR50AE)[1,1],t(MCAR10AE)[1,4],t(MCAR30AE)[1,4],t(MCAR50AE)[1,4])
tab1MCAR <- rbind(tab1MCAR,AEBiasMSE)
rownames(tab1MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab1MAR10 <-t(MAR10[c(1,4),TreatInds])
tab1MAR30 <- t(MAR30[c(1,4),TreatInds])
tab1MAR50 <- t(MAR50[c(1,4),TreatInds])
tab1MAR <- cbind(tab1MAR10[,1],tab1MAR30[,1],tab1MAR50[,1],tab1MAR10[,2],tab1MAR30[,2],tab1MAR50[,2])

AEBiasMSE <- cbind(t(MAR10AE)[1,1],t(MAR30AE)[1,1],t(MAR50AE)[1,1],t(MAR10AE)[1,4],t(MAR30AE)[1,4],t(MAR50AE)[1,4])
tab1MAR <- rbind(tab1MAR,AEBiasMSE)
rownames(tab1MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab1MNAR10a <-t(MNAR10a[c(1,4),TreatInds])
tab1MNAR30a <- t(MNAR30a[c(1,4),TreatInds])
tab1MNAR50a <- t(MNAR50a[c(1,4),TreatInds])
tab1MNARa <- cbind(tab1MNAR10a[,1],tab1MNAR30a[,1],tab1MNAR50a[,1],tab1MNAR10a[,2],tab1MNAR30a[,2],tab1MNAR50a[,2])

AEBiasMSEa <- cbind(t(MNAR10aAE)[1,1],t(MNAR30aAE)[1,1],t(MNAR50aAE)[1,1],t(MNAR10aAE)[1,4],t(MNAR30aAE)[1,4],t(MNAR50aAE)[1,4])
tab1MNARa <- rbind(tab1MNARa,AEBiasMSEa)
rownames(tab1MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab1MNAR10b <-t(MNAR10b[c(1,4),TreatInds])
tab1MNAR30b <- t(MNAR30b[c(1,4),TreatInds])
tab1MNAR50b <- t(MNAR50b[c(1,4),TreatInds])
tab1MNARb <- cbind(tab1MNAR10b[,1],tab1MNAR30b[,1],tab1MNAR50b[,1],tab1MNAR10b[,2],tab1MNAR30b[,2],tab1MNAR50b[,2])

AEBiasMSEb <- cbind(t(MNAR10bAE)[1,1],t(MNAR30bAE)[1,1],t(MNAR50bAE)[1,1],t(MNAR10bAE)[1,4],t(MNAR30bAE)[1,4],t(MNAR50bAE)[1,4])
tab1MNARb <- rbind(tab1MNARb,AEBiasMSEb)
rownames(tab1MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab1final <- rbind(tab1MCAR,tab1MAR,tab1MNARa,tab1MNARb)
print(tab1final)

# Table 2: Treat SE and coverage
tab2MCAR10 <-t(MCAR10[c(2,3),TreatInds])
tab2MCAR30 <- t(MCAR30[c(2,3),TreatInds])
tab2MCAR50 <- t(MCAR50[c(2,3),TreatInds])
tab2MCAR <- cbind(tab2MCAR10[,1],tab2MCAR30[,1],tab2MCAR50[,1],tab2MCAR10[,2],tab2MCAR30[,2],tab2MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab2MCAR <- rbind(prop,tab2MCAR)

AEseCov <- cbind(t(MCAR10AE)[1,2],t(MCAR30AE)[1,2],t(MCAR50AE)[1,2],t(MCAR10AE)[1,3],t(MCAR30AE)[1,3],t(MCAR50AE)[1,3])
tab2MCAR <- rbind(tab2MCAR,AEseCov)
rownames(tab2MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab2MAR10 <-t(MAR10[c(2,3),TreatInds])
tab2MAR30 <- t(MAR30[c(2,3),TreatInds])
tab2MAR50 <- t(MAR50[c(2,3),TreatInds])
tab2MAR <- cbind(tab2MAR10[,1],tab2MAR30[,1],tab2MAR50[,1],tab2MAR10[,2],tab2MAR30[,2],tab2MAR50[,2])

AEseCov <- cbind(t(MAR10AE)[1,2],t(MAR30AE)[1,2],t(MAR50AE)[1,2],t(MAR10AE)[1,3],t(MAR30AE)[1,3],t(MAR50AE)[1,3])
tab2MAR <- rbind(tab2MAR,AEseCov)
rownames(tab2MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab2MNAR10a <-t(MNAR10a[c(2,3),TreatInds])
tab2MNAR30a <- t(MNAR30a[c(2,3),TreatInds])
tab2MNAR50a <- t(MNAR50a[c(2,3),TreatInds])
tab2MNARa <- cbind(tab2MNAR10a[,1],tab2MNAR30a[,1],tab2MNAR50a[,1],tab2MNAR10a[,2],tab2MNAR30a[,2],tab2MNAR50a[,2])

AEseCov <- cbind(t(MNAR10aAE)[1,2],t(MNAR30aAE)[1,2],t(MNAR50aAE)[1,2],t(MNAR10aAE)[1,3],t(MNAR30aAE)[1,3],t(MNAR50aAE)[1,3])
tab2MNARa <- rbind(tab2MNARa,AEseCov)
rownames(tab2MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab2MNAR10b <-t(MNAR10b[c(2,3),TreatInds])
tab2MNAR30b <- t(MNAR30b[c(2,3),TreatInds])
tab2MNAR50b <- t(MNAR50b[c(2,3),TreatInds])
tab2MNARb <- cbind(tab2MNAR10b[,1],tab2MNAR30b[,1],tab2MNAR50b[,1],tab2MNAR10b[,2],tab2MNAR30b[,2],tab2MNAR50b[,2])

AEseCov <- cbind(t(MNAR10bAE)[1,2],t(MNAR30bAE)[1,2],t(MNAR50bAE)[1,2],t(MNAR10bAE)[1,3],t(MNAR30bAE)[1,3],t(MNAR50bAE)[1,3])
tab2MNARb <- rbind(tab2MNARb,AEseCov)
rownames(tab2MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab2final <- rbind(tab2MCAR,tab2MAR,tab2MNARa,tab2MNARb)
print(tab2final)

tab1Treat <- round (tab1final, 4)
tab2Treat <- round (tab2final, 4)
tab1Treat = tab1Treat[-c (1,7,12,17),]
tab2Treat = tab2Treat[-c (1,7,12,17),]
```

\newpage

# Treat
```{r echo=FALSE}
lsep = c("\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "")

kable(tab1Treat, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Treatment") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "Bias"=3, "MSE"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

\newpage

```{r echo=FALSE}
kable(tab2Treat, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Treatment") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "SE"=3, "Coverage"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```


```{r echo=F, include=F}
# Table 3: ECOG Bias and MSE
tab3MCAR10 <-t(MCAR10[c(1,4),EcogInds])
tab3MCAR30 <- t(MCAR30[c(1,4),EcogInds])
tab3MCAR50 <- t(MCAR50[c(1,4),EcogInds])
tab3MCAR <- cbind(tab3MCAR10[,1],tab3MCAR30[,1],tab3MCAR50[,1],tab3MCAR10[,2],tab3MCAR30[,2],tab3MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab3MCAR <- rbind(prop,tab3MCAR)

AEBiasMSE <- cbind(t(MCAR10AE)[2,1],t(MCAR30AE)[2,1],t(MCAR50AE)[2,1],t(MCAR10AE)[2,4],t(MCAR30AE)[2,4],t(MCAR50AE)[2,4])
tab3MCAR <- rbind(tab3MCAR,AEBiasMSE)
rownames(tab3MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab3MAR10 <-t(MAR10[c(1,4),EcogInds])
tab3MAR30 <- t(MAR30[c(1,4),EcogInds])
tab3MAR50 <- t(MAR50[c(1,4),EcogInds])
tab3MAR <- cbind(tab3MAR10[,1],tab3MAR30[,1],tab3MAR50[,1],tab3MAR10[,2],tab3MAR30[,2],tab3MAR50[,2])

AEBiasMSE <- cbind(t(MAR10AE)[2,1],t(MAR30AE)[2,1],t(MAR50AE)[2,1],t(MAR10AE)[2,4],t(MAR30AE)[2,4],t(MAR50AE)[2,4])
tab3MAR <- rbind(tab3MAR,AEBiasMSE)
rownames(tab3MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab3MNAR10a <-t(MNAR10a[c(1,4),EcogInds])
tab3MNAR30a <- t(MNAR30a[c(1,4),EcogInds])
tab3MNAR50a <- t(MNAR50a[c(1,4),EcogInds])
tab3MNARa <- cbind(tab3MNAR10a[,1],tab3MNAR30a[,1],tab3MNAR50a[,1],tab3MNAR10a[,2],tab3MNAR30a[,2],tab3MNAR50a[,2])

AEBiasMSEa <- cbind(t(MNAR10aAE)[2,1],t(MNAR30aAE)[2,1],t(MNAR50aAE)[2,1],t(MNAR10aAE)[2,4],t(MNAR30aAE)[2,4],t(MNAR50aAE)[2,4])
tab3MNARa <- rbind(tab3MNARa,AEBiasMSEa)
rownames(tab3MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab3MNAR10b <-t(MNAR10b[c(1,4),EcogInds])
tab3MNAR30b <- t(MNAR30b[c(1,4),EcogInds])
tab3MNAR50b <- t(MNAR50b[c(1,4),EcogInds])
tab3MNARb <- cbind(tab3MNAR10b[,1],tab3MNAR30b[,1],tab3MNAR50b[,1],tab3MNAR10b[,2],tab3MNAR30b[,2],tab3MNAR50b[,2])

AEBiasMSEb <- cbind(t(MNAR10bAE)[2,1],t(MNAR30bAE)[2,1],t(MNAR50bAE)[2,1],t(MNAR10bAE)[2,4],t(MNAR30bAE)[2,4],t(MNAR50bAE)[2,4])
tab3MNARb <- rbind(tab3MNARb,AEBiasMSEb)
rownames(tab3MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab3final <- rbind(tab3MCAR,tab3MAR,tab3MNARa,tab3MNARb)
print(tab3final)

# Table 4: ECOG SE and coverage
tab4MCAR10 <-t(MCAR10[c(2,3),EcogInds])
tab4MCAR30 <- t(MCAR30[c(2,3),EcogInds])
tab4MCAR50 <- t(MCAR50[c(2,3),EcogInds])
tab4MCAR <- cbind(tab4MCAR10[,1],tab4MCAR30[,1],tab4MCAR50[,1],tab4MCAR10[,2],tab4MCAR30[,2],tab4MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab4MCAR <- rbind(prop,tab4MCAR)

AEseCov <- cbind(t(MCAR10AE)[2,2],t(MCAR30AE)[2,2],t(MCAR50AE)[2,2],t(MCAR10AE)[2,3],t(MCAR30AE)[2,3],t(MCAR50AE)[2,3])
tab4MCAR <- rbind(tab4MCAR,AEseCov)
rownames(tab4MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab4MAR10 <-t(MAR10[c(2,3),EcogInds])
tab4MAR30 <- t(MAR30[c(2,3),EcogInds])
tab4MAR50 <- t(MAR50[c(2,3),EcogInds])
tab4MAR <- cbind(tab4MAR10[,1],tab4MAR30[,1],tab4MAR50[,1],tab4MAR10[,2],tab4MAR30[,2],tab4MAR50[,2])

AEseCov <- cbind(t(MAR10AE)[2,2],t(MAR30AE)[2,2],t(MAR50AE)[2,2],t(MAR10AE)[2,3],t(MAR30AE)[2,3],t(MAR50AE)[2,3])
tab4MAR <- rbind(tab4MAR,AEseCov)
rownames(tab4MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab4MNAR10a <-t(MNAR10a[c(2,3),EcogInds])
tab4MNAR30a <- t(MNAR30a[c(2,3),EcogInds])
tab4MNAR50a <- t(MNAR50a[c(2,3),EcogInds])
tab4MNARa <- cbind(tab4MNAR10a[,1],tab4MNAR30a[,1],tab4MNAR50a[,1],tab4MNAR10a[,2],tab4MNAR30a[,2],tab4MNAR50a[,2])

AEseCov <- cbind(t(MNAR10aAE)[2,2],t(MNAR30aAE)[2,2],t(MNAR50aAE)[2,2],t(MNAR10aAE)[2,3],t(MNAR30aAE)[2,3],t(MNAR50aAE)[2,3])
tab4MNARa <- rbind(tab4MNARa,AEseCov)
rownames(tab4MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab4MNAR10b <-t(MNAR10b[c(2,3),EcogInds])
tab4MNAR30b <- t(MNAR30b[c(2,3),EcogInds])
tab4MNAR50b <- t(MNAR50b[c(2,3),EcogInds])
tab4MNARb <- cbind(tab4MNAR10b[,1],tab4MNAR30b[,1],tab4MNAR50b[,1],tab4MNAR10b[,2],tab4MNAR30b[,2],tab4MNAR50b[,2])

AEseCov <- cbind(t(MNAR10bAE)[2,2],t(MNAR30bAE)[2,2],t(MNAR50bAE)[2,2],t(MNAR10bAE)[2,3],t(MNAR30bAE)[2,3],t(MNAR50bAE)[2,3])
tab4MNARb <- rbind(tab4MNARb,AEseCov)
rownames(tab4MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab4final <- rbind(tab4MCAR,tab4MAR,tab4MNARa,tab4MNARb)
print(tab4final)

tab3Ecog <- round (tab3final, 4)
tab4Ecog <- round (tab4final, 4)
tab3Ecog = tab3Ecog[-c (1,7,12,17),]
tab4Ecog = tab4Ecog[-c (1,7,12,17),]
```

\newpage 

# ECOG 
```{r echo=FALSE}
kable(tab3Ecog, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "ECOG") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "Bias"=3, "MSE"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

\newpage 

```{r echo=FALSE}
kable(tab4Ecog, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "ECOG") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "SE"=3, "Coverage"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

```{r echo=F, include=F}
# Table 5: Var1 Bias and MSE
tab5MCAR10 <-t(MCAR10[c(1,4),Var1Inds])
tab5MCAR30 <- t(MCAR30[c(1,4),Var1Inds])
tab5MCAR50 <- t(MCAR50[c(1,4),Var1Inds])
tab5MCAR <- cbind(tab5MCAR10[,1],tab5MCAR30[,1],tab5MCAR50[,1],tab5MCAR10[,2],tab5MCAR30[,2],tab5MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab5MCAR <- rbind(prop,tab5MCAR)

AEBiasMSE <- cbind(t(MCAR10AE)[2,1],t(MCAR30AE)[2,1],t(MCAR50AE)[2,1],t(MCAR10AE)[2,4],t(MCAR30AE)[2,4],t(MCAR50AE)[2,4])
tab5MCAR <- rbind(tab5MCAR,AEBiasMSE)
rownames(tab5MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab5MAR10 <-t(MAR10[c(1,4),Var1Inds])
tab5MAR30 <- t(MAR30[c(1,4),Var1Inds])
tab5MAR50 <- t(MAR50[c(1,4),Var1Inds])
tab5MAR <- cbind(tab5MAR10[,1],tab5MAR30[,1],tab5MAR50[,1],tab5MAR10[,2],tab5MAR30[,2],tab5MAR50[,2])

AEBiasMSE <- cbind(t(MAR10AE)[2,1],t(MAR30AE)[2,1],t(MAR50AE)[2,1],t(MAR10AE)[2,4],t(MAR30AE)[2,4],t(MAR50AE)[2,4])
tab5MAR <- rbind(tab5MAR,AEBiasMSE)
rownames(tab5MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab5MNAR10a <-t(MNAR10a[c(1,4),Var1Inds])
tab5MNAR30a <- t(MNAR30a[c(1,4),Var1Inds])
tab5MNAR50a <- t(MNAR50a[c(1,4),Var1Inds])
tab5MNARa <- cbind(tab5MNAR10a[,1],tab5MNAR30a[,1],tab5MNAR50a[,1],tab5MNAR10a[,2],tab5MNAR30a[,2],tab5MNAR50a[,2])

AEBiasMSEa <- cbind(t(MNAR10aAE)[2,1],t(MNAR30aAE)[2,1],t(MNAR50aAE)[2,1],t(MNAR10aAE)[2,4],t(MNAR30aAE)[2,4],t(MNAR50aAE)[2,4])
tab5MNARa <- rbind(tab5MNARa,AEBiasMSEa)
rownames(tab5MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab5MNAR10b <-t(MNAR10b[c(1,4),Var1Inds])
tab5MNAR30b <- t(MNAR30b[c(1,4),Var1Inds])
tab5MNAR50b <- t(MNAR50b[c(1,4),Var1Inds])
tab5MNARb <- cbind(tab5MNAR10b[,1],tab5MNAR30b[,1],tab5MNAR50b[,1],tab5MNAR10b[,2],tab5MNAR30b[,2],tab5MNAR50b[,2])

AEBiasMSEb <- cbind(t(MNAR10bAE)[2,1],t(MNAR30bAE)[2,1],t(MNAR50bAE)[2,1],t(MNAR10bAE)[2,4],t(MNAR30bAE)[2,4],t(MNAR50bAE)[2,4])
tab5MNARb <- rbind(tab5MNARb,AEBiasMSEb)
rownames(tab5MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab5final <- rbind(tab5MCAR,tab5MAR,tab5MNARa,tab5MNARb)
print(tab5final)

# Table 6: Var1 SE and coverage
tab6MCAR10 <-t(MCAR10[c(2,3),Var1Inds])
tab6MCAR30 <- t(MCAR30[c(2,3),Var1Inds])
tab6MCAR50 <- t(MCAR50[c(2,3),Var1Inds])
tab6MCAR <- cbind(tab6MCAR10[,1],tab6MCAR30[,1],tab6MCAR50[,1],tab6MCAR10[,2],tab6MCAR30[,2],tab6MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab6MCAR <- rbind(prop,tab6MCAR)

AEseCov <- cbind(t(MCAR10AE)[2,2],t(MCAR30AE)[2,2],t(MCAR50AE)[2,2],t(MCAR10AE)[2,3],t(MCAR30AE)[2,3],t(MCAR50AE)[2,3])
tab6MCAR <- rbind(tab6MCAR,AEseCov)
rownames(tab6MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab6MAR10 <-t(MAR10[c(2,3),Var1Inds])
tab6MAR30 <- t(MAR30[c(2,3),Var1Inds])
tab6MAR50 <- t(MAR50[c(2,3),Var1Inds])
tab6MAR <- cbind(tab6MAR10[,1],tab6MAR30[,1],tab6MAR50[,1],tab6MAR10[,2],tab6MAR30[,2],tab6MAR50[,2])

AEseCov <- cbind(t(MAR10AE)[2,2],t(MAR30AE)[2,2],t(MAR50AE)[2,2],t(MAR10AE)[2,3],t(MAR30AE)[2,3],t(MAR50AE)[2,3])
tab6MAR <- rbind(tab6MAR,AEseCov)
rownames(tab6MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab6MNAR10a <-t(MNAR10a[c(2,3),Var1Inds])
tab6MNAR30a <- t(MNAR30a[c(2,3),Var1Inds])
tab6MNAR50a <- t(MNAR50a[c(2,3),Var1Inds])
tab6MNARa <- cbind(tab6MNAR10a[,1],tab6MNAR30a[,1],tab6MNAR50a[,1],tab6MNAR10a[,2],tab6MNAR30a[,2],tab6MNAR50a[,2])

AEseCov <- cbind(t(MNAR10aAE)[2,2],t(MNAR30aAE)[2,2],t(MNAR50aAE)[2,2],t(MNAR10aAE)[2,3],t(MNAR30aAE)[2,3],t(MNAR50aAE)[2,3])
tab6MNARa <- rbind(tab6MNARa,AEseCov)
rownames(tab6MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab6MNAR10b <-t(MNAR10b[c(2,3),Var1Inds])
tab6MNAR30b <- t(MNAR30b[c(2,3),Var1Inds])
tab6MNAR50b <- t(MNAR50b[c(2,3),Var1Inds])
tab6MNARb <- cbind(tab6MNAR10b[,1],tab6MNAR30b[,1],tab6MNAR50b[,1],tab6MNAR10b[,2],tab6MNAR30b[,2],tab6MNAR50b[,2])

AEseCov <- cbind(t(MNAR10bAE)[2,2],t(MNAR30bAE)[2,2],t(MNAR50bAE)[2,2],t(MNAR10bAE)[2,3],t(MNAR30bAE)[2,3],t(MNAR50bAE)[2,3])
tab6MNARb <- rbind(tab6MNARb,AEseCov)
rownames(tab6MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab6final <- rbind(tab6MCAR,tab6MAR,tab6MNARa,tab6MNARb)
print(tab6final)

tab5Var1 <- round (tab5final, 4)
tab6Var1 <- round (tab6final, 4)
tab5Var1 = tab5Var1[-c (1,7,12,17),]
tab6Var1 = tab6Var1[-c (1,7,12,17),]
```

\newpage 

# Var 1
```{r echo=FALSE}
kable(tab5Var1, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Var 1") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "Bias"=3, "MSE"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

\newpage 

```{r echo=FALSE}
kable(tab6Var1, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Var 1") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "SE"=3, "Coverage"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

```{r echo=F, include=F}
# Table 7: Var2 Bias and MSE
tab7MCAR10 <-t(MCAR10[c(1,4),Var2Inds])
tab7MCAR30 <- t(MCAR30[c(1,4),Var2Inds])
tab7MCAR50 <- t(MCAR50[c(1,4),Var2Inds])
tab7MCAR <- cbind(tab7MCAR10[,1],tab7MCAR30[,1],tab7MCAR50[,1],tab7MCAR10[,2],tab7MCAR30[,2],tab7MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab7MCAR <- rbind(prop,tab7MCAR)

AEBiasMSE <- cbind(t(MCAR10AE)[2,1],t(MCAR30AE)[2,1],t(MCAR50AE)[2,1],t(MCAR10AE)[2,4],t(MCAR30AE)[2,4],t(MCAR50AE)[2,4])
tab7MCAR <- rbind(tab7MCAR,AEBiasMSE)
rownames(tab7MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab7MAR10 <-t(MAR10[c(1,4),Var2Inds])
tab7MAR30 <- t(MAR30[c(1,4),Var2Inds])
tab7MAR50 <- t(MAR50[c(1,4),Var2Inds])
tab7MAR <- cbind(tab7MAR10[,1],tab7MAR30[,1],tab7MAR50[,1],tab7MAR10[,2],tab7MAR30[,2],tab7MAR50[,2])

AEBiasMSE <- cbind(t(MAR10AE)[2,1],t(MAR30AE)[2,1],t(MAR50AE)[2,1],t(MAR10AE)[2,4],t(MAR30AE)[2,4],t(MAR50AE)[2,4])
tab7MAR <- rbind(tab7MAR,AEBiasMSE)
rownames(tab7MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab7MNAR10a <-t(MNAR10a[c(1,4),Var2Inds])
tab7MNAR30a <- t(MNAR30a[c(1,4),Var2Inds])
tab7MNAR50a <- t(MNAR50a[c(1,4),Var2Inds])
tab7MNARa <- cbind(tab7MNAR10a[,1],tab7MNAR30a[,1],tab7MNAR50a[,1],tab7MNAR10a[,2],tab7MNAR30a[,2],tab7MNAR50a[,2])

AEBiasMSEa <- cbind(t(MNAR10aAE)[2,1],t(MNAR30aAE)[2,1],t(MNAR50aAE)[2,1],t(MNAR10aAE)[2,4],t(MNAR30aAE)[2,4],t(MNAR50aAE)[2,4])
tab7MNARa <- rbind(tab7MNARa,AEBiasMSEa)
rownames(tab7MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab7MNAR10b <-t(MNAR10b[c(1,4),Var2Inds])
tab7MNAR30b <- t(MNAR30b[c(1,4),Var2Inds])
tab7MNAR50b <- t(MNAR50b[c(1,4),Var2Inds])
tab7MNARb <- cbind(tab7MNAR10b[,1],tab7MNAR30b[,1],tab7MNAR50b[,1],tab7MNAR10b[,2],tab7MNAR30b[,2],tab7MNAR50b[,2])

AEBiasMSEb <- cbind(t(MNAR10bAE)[2,1],t(MNAR30bAE)[2,1],t(MNAR50bAE)[2,1],t(MNAR10bAE)[2,4],t(MNAR30bAE)[2,4],t(MNAR50bAE)[2,4])
tab7MNARb <- rbind(tab7MNARb,AEBiasMSEb)
rownames(tab7MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab7final <- rbind(tab7MCAR,tab7MAR,tab7MNARa,tab7MNARb)
print(tab7final)

# Table 8: Var2 SE and coverage
tab8MCAR10 <-t(MCAR10[c(2,3),Var2Inds])
tab8MCAR30 <- t(MCAR30[c(2,3),Var2Inds])
tab8MCAR50 <- t(MCAR50[c(2,3),Var2Inds])
tab8MCAR <- cbind(tab8MCAR10[,1],tab8MCAR30[,1],tab8MCAR50[,1],tab8MCAR10[,2],tab8MCAR30[,2],tab8MCAR50[,2])
prop <- c(10,30,50,10,30,50)
tab8MCAR <- rbind(prop,tab8MCAR)

AEseCov <- cbind(t(MCAR10AE)[2,2],t(MCAR30AE)[2,2],t(MCAR50AE)[2,2],t(MCAR10AE)[2,3],t(MCAR30AE)[2,3],t(MCAR50AE)[2,3])
tab8MCAR <- rbind(tab8MCAR,AEseCov)
rownames(tab8MCAR) <- c("prop","ORACLE", "CC", "MICE", "RF", "DAE")

tab8MAR10 <-t(MAR10[c(2,3),Var2Inds])
tab8MAR30 <- t(MAR30[c(2,3),Var2Inds])
tab8MAR50 <- t(MAR50[c(2,3),Var2Inds])
tab8MAR <- cbind(tab8MAR10[,1],tab8MAR30[,1],tab8MAR50[,1],tab8MAR10[,2],tab8MAR30[,2],tab8MAR50[,2])

AEseCov <- cbind(t(MAR10AE)[2,2],t(MAR30AE)[2,2],t(MAR50AE)[2,2],t(MAR10AE)[2,3],t(MAR30AE)[2,3],t(MAR50AE)[2,3])
tab8MAR <- rbind(tab8MAR,AEseCov)
rownames(tab8MAR) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab8MNAR10a <-t(MNAR10a[c(2,3),Var2Inds])
tab8MNAR30a <- t(MNAR30a[c(2,3),Var2Inds])
tab8MNAR50a <- t(MNAR50a[c(2,3),Var2Inds])
tab8MNARa <- cbind(tab8MNAR10a[,1],tab8MNAR30a[,1],tab8MNAR50a[,1],tab8MNAR10a[,2],tab8MNAR30a[,2],tab8MNAR50a[,2])

AEseCov <- cbind(t(MNAR10aAE)[2,2],t(MNAR30aAE)[2,2],t(MNAR50aAE)[2,2],t(MNAR10aAE)[2,3],t(MNAR30aAE)[2,3],t(MNAR50aAE)[2,3])
tab8MNARa <- rbind(tab8MNARa,AEseCov)
rownames(tab8MNARa) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab8MNAR10b <-t(MNAR10b[c(2,3),Var2Inds])
tab8MNAR30b <- t(MNAR30b[c(2,3),Var2Inds])
tab8MNAR50b <- t(MNAR50b[c(2,3),Var2Inds])
tab8MNARb <- cbind(tab8MNAR10b[,1],tab8MNAR30b[,1],tab8MNAR50b[,1],tab8MNAR10b[,2],tab8MNAR30b[,2],tab8MNAR50b[,2])

AEseCov <- cbind(t(MNAR10bAE)[2,2],t(MNAR30bAE)[2,2],t(MNAR50bAE)[2,2],t(MNAR10bAE)[2,3],t(MNAR30bAE)[2,3],t(MNAR50bAE)[2,3])
tab8MNARb <- rbind(tab8MNARb,AEseCov)
rownames(tab8MNARb) <- c("ORACLE", "CC", "MICE", "RF", "DAE")

tab8final <- rbind(tab8MCAR,tab8MAR,tab8MNARa,tab8MNARb)
print(tab8final)

tab7Var2 <- round (tab7final, 4)
tab8Var2 <- round (tab8final, 4)
tab7Var2 = tab7Var2[-c (1,7,12,17),]
tab8Var2 = tab8Var2[-c (1,7,12,17),]
```

\newpage

# Var 2
```{r echo=FALSE}
kable(tab7Var2, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Var 2") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "Bias"=3, "MSE"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```

\newpage

```{r echo=FALSE}
kable(tab8Var2, row.names=TRUE, align=c("l", "c", "c", "c", "c", "c", "c"), format = "latex", booktabs = T, linesep = lsep, caption = "Var 2") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  add_header_above(c(" "=1, "Low"=1, "Medium"=1, "High"=1, "Low"=1, "Medium"=1, "High"=1)) %>% add_header_above(c(" "=1, "SE"=3, "Coverage"=3)) %>% group_rows (index=c (" "=1, "MCAR"=4, "MAR"=4, "MNAR 1"=4, "MNAR 2"=4))
```


\newpage

```{r,echo=F}
TreatInds = c(1,5,9,13,17)
EcogInds = c(2,6,10,14,18)
Var1Inds = c(3,7,11,15,19)
Var2Inds = c(4,8,12,16,20)
```

# Treat Percentiles of Est - Truth
```{r,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercTreatMCAR[c(1,3,5,7,9),1],PercTreatMCAR[c(1,3,5,7,9),2],PercTreatMCAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercTreatMCAR[c(2,4,6,8,10),1],PercTreatMCAR[c(2,4,6,8,10),2],PercTreatMCAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()

dfMCAR<- data.frame(bias=rbind(t(MCAR10Full[1,TreatInds]),t(MCAR30Full[1,TreatInds]),t(MCAR50Full[1,TreatInds])),sd=rbind(t(MCAR10Full[2,TreatInds]),t(MCAR30Full[2,TreatInds]),t(MCAR50Full[2,TreatInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMCAR)
dfMCAR <- cbind(dfMCAR,feats)
dfMCAR$feats <- factor(dfMCAR$feats, levels = dfMCAR$feats[order(dfMCAR$prop)])

dfMCAR <- dfMCAR[-c(6,11),]
dfMCAR$prop <- as.character(dfMCAR$prop)
dfMCAR[1,6]<- ""
dfMCAR$group <- as.character(dfMCAR$group)
dfMCAR$group <- factor(dfMCAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMCAR <- ggplot(dfMCAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercTreatMAR[c(1,3,5,7,9),1],PercTreatMAR[c(1,3,5,7,9),2],PercTreatMAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercTreatMAR[c(2,4,6,8,10),1],PercTreatMAR[c(2,4,6,8,10),2],PercTreatMAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMAR<- data.frame(bias=rbind(t(MAR10Full[1,TreatInds]),t(MAR30Full[1,TreatInds]),t(MAR50Full[1,TreatInds])),sd=rbind(t(MAR10Full[2,TreatInds]),t(MAR30Full[2,TreatInds]),t(MAR50Full[2,TreatInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMAR)
dfMAR <- cbind(dfMAR,feats)
dfMAR$feats <- factor(dfMAR$feats, levels = dfMAR$feats[order(dfMAR$prop)])

dfMAR <- dfMAR[-c(6,11),]
dfMAR$prop <- as.character(dfMAR$prop)
dfMAR[1,6]<- ""
dfMAR$group <- as.character(dfMAR$group)
dfMAR$group <- factor(dfMAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMAR <- ggplot(dfMAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercTreatMNAR1[c(1,3,5,7,9),1],PercTreatMNAR1[c(1,3,5,7,9),2],PercTreatMNAR1[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercTreatMNAR1[c(2,4,6,8,10),1],PercTreatMNAR1[c(2,4,6,8,10),2],PercTreatMNAR1[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10aFull[1,TreatInds]),t(MNAR30aFull[1,TreatInds]),t(MNAR50aFull[1,TreatInds])),sd=rbind(t(MNAR10aFull[2,TreatInds]),t(MNAR30aFull[2,TreatInds]),t(MNAR50aFull[2,TreatInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR1 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercTreatMNAR2[c(1,3,5,7,9),1],PercTreatMNAR2[c(1,3,5,7,9),2],PercTreatMNAR2[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercTreatMNAR2[c(2,4,6,8,10),1],PercTreatMNAR2[c(2,4,6,8,10),2],PercTreatMNAR2[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10bFull[1,TreatInds]),t(MNAR30bFull[1,TreatInds]),t(MNAR50bFull[1,TreatInds])),sd=rbind(t(MNAR10bFull[2,TreatInds]),t(MNAR30bFull[2,TreatInds]),t(MNAR50bFull[2,TreatInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR2 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{r,echo=F}
library (gridExtra)

plotMCAR = plotMCAR + ggtitle("MCAR")
plotMAR = plotMAR + ggtitle("MAR")
plotMNAR1 = plotMNAR1 + ggtitle("MNAR1")
plotMNAR2 = plotMNAR2 + ggtitle("MNAR2")
plotTxt = grid.arrange(plotMCAR, plotMAR, plotMNAR1, plotMNAR2, nrow = 2)
#plot (plotTxt)

png('~/Desktop/plotAllTreat.png', width=10, height=8, units="in", pointsize=2, res=300)
plot (plotTxt)
dev.off()

```

<!--

```{r,echo=F}
if(FALSE){
dfMCAR$mech = 'MCAR'
dfMAR$mech = 'MAR'
dfMNAR$mech = 'MNAR'
tdf = rbind (dfMCAR, dfMAR, dfMNAR)
tdf$mech = factor (tdf$mech, levels=c("MCAR", "MAR", "MNAR"))

plotTxt <- ggplot(tdf, aes(x = group, y=bias, color = group))+
  ylim(lowerlim, upperlim)+
  ylab("Bias")+ 
  xlab("")+
  geom_errorbar(aes(ymax = upper, ymin = lower),
                position = "dodge", size = 1.5)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  geom_point(shape=16, colour="black", size=2)+
  facet_grid(cols=vars(prop), rows=vars(mech), 
             scales="free_x", space="free_x")+
  theme(legend.position = 'none', 
        panel.spacing = unit(1, "lines"),
        strip.background = element_blank(),
        axis.line = element_line(colour = "grey"),
        panel.grid.major.y = element_line(colour = "grey"),
        strip.placement = "outside",
        axis.text.x = element_text(angle = 45, hjust = 1,size=10),
        panel.background = element_rect(fill = 'white', colour = 'white'))+
  scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+
  scale_color_manual(values=mycols)+
  facet_wrap(~mech, nrow = 3)


png('~/Desktop/plotAllTreat.png', width=5, height=12, units="in", pointsize=2, res=300)
plotTxt
dev.off()

}

```

-->


\newpage

# Ecog Percentiles of Est - Truth
```{r,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercEcogMCAR[c(1,3,5,7,9),1],PercEcogMCAR[c(1,3,5,7,9),2],PercEcogMCAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercEcogMCAR[c(2,4,6,8,10),1],PercEcogMCAR[c(2,4,6,8,10),2],PercEcogMCAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMCAR<- data.frame(bias=rbind(t(MCAR10Full[1,EcogInds]),t(MCAR30Full[1,EcogInds]),t(MCAR50Full[1,EcogInds])),sd=rbind(t(MCAR10Full[2,EcogInds]),t(MCAR30Full[2,EcogInds]),t(MCAR50Full[2,EcogInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMCAR)
dfMCAR <- cbind(dfMCAR,feats)
dfMCAR$feats <- factor(dfMCAR$feats, levels = dfMCAR$feats[order(dfMCAR$prop)])

dfMCAR <- dfMCAR[-c(6,11),]
dfMCAR$prop <- as.character(dfMCAR$prop)
dfMCAR[1,6]<- ""
dfMCAR$group <- as.character(dfMCAR$group)
dfMCAR$group <- factor(dfMCAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMCAR <- ggplot(dfMCAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercEcogMAR[c(1,3,5,7,9),1],PercEcogMAR[c(1,3,5,7,9),2],PercEcogMAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercEcogMAR[c(2,4,6,8,10),1],PercEcogMAR[c(2,4,6,8,10),2],PercEcogMAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMAR<- data.frame(bias=rbind(t(MAR10Full[1,EcogInds]),t(MAR30Full[1,EcogInds]),t(MAR50Full[1,EcogInds])),sd=rbind(t(MAR10Full[2,EcogInds]),t(MAR30Full[2,EcogInds]),t(MAR50Full[2,EcogInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMAR)
dfMAR <- cbind(dfMAR,feats)
dfMAR$feats <- factor(dfMAR$feats, levels = dfMAR$feats[order(dfMAR$prop)])

dfMAR <- dfMAR[-c(6,11),]
dfMAR$prop <- as.character(dfMAR$prop)
dfMAR[1,6]<- ""
dfMAR$group <- as.character(dfMAR$group)
dfMAR$group <- factor(dfMAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMAR <- ggplot(dfMAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercEcogMNAR1[c(1,3,5,7,9),1],PercEcogMNAR1[c(1,3,5,7,9),2],PercEcogMNAR1[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercEcogMNAR1[c(2,4,6,8,10),1],PercEcogMNAR1[c(2,4,6,8,10),2],PercEcogMNAR1[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10aFull[1,EcogInds]),t(MNAR30aFull[1,EcogInds]),t(MNAR50aFull[1,EcogInds])),sd=rbind(t(MNAR10aFull[2,EcogInds]),t(MNAR30aFull[2,EcogInds]),t(MNAR50aFull[2,EcogInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR1 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercEcogMNAR2[c(1,3,5,7,9),1],PercEcogMNAR2[c(1,3,5,7,9),2],PercEcogMNAR2[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercEcogMNAR2[c(2,4,6,8,10),1],PercEcogMNAR2[c(2,4,6,8,10),2],PercEcogMNAR2[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10bFull[1,EcogInds]),t(MNAR30bFull[1,EcogInds]),t(MNAR50bFull[1,EcogInds])),sd=rbind(t(MNAR10bFull[2,EcogInds]),t(MNAR30bFull[2,EcogInds]),t(MNAR50bFull[2,EcogInds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR2 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{r,echo=F}
library (gridExtra)

plotMCAR = plotMCAR + ggtitle("MCAR")
plotMAR = plotMAR + ggtitle("MAR")
plotMNAR1 = plotMNAR1 + ggtitle("MNAR1")
plotMNAR2 = plotMNAR2 + ggtitle("MNAR2")
plotTxt = grid.arrange(plotMCAR, plotMAR, plotMNAR1, plotMNAR2, nrow = 2)
#plot (plotTxt)

png('~/Desktop/plotAllEcog.png', width=10, height=8, units="in", pointsize=2, res=300)
plot (plotTxt)
dev.off()

```






\newpage

# Var1 Percentiles of Est - Truth
```{r,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar1MCAR[c(1,3,5,7,9),1],PercVar1MCAR[c(1,3,5,7,9),2],PercVar1MCAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar1MCAR[c(2,4,6,8,10),1],PercVar1MCAR[c(2,4,6,8,10),2],PercVar1MCAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMCAR<- data.frame(bias=rbind(t(MCAR10Full[1,Var1Inds]),t(MCAR30Full[1,Var1Inds]),t(MCAR50Full[1,Var1Inds])),sd=rbind(t(MCAR10Full[2,Var1Inds]),t(MCAR30Full[2,Var1Inds]),t(MCAR50Full[2,Var1Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMCAR)
dfMCAR <- cbind(dfMCAR,feats)
dfMCAR$feats <- factor(dfMCAR$feats, levels = dfMCAR$feats[order(dfMCAR$prop)])

dfMCAR <- dfMCAR[-c(6,11),]
dfMCAR$prop <- as.character(dfMCAR$prop)
dfMCAR[1,6]<- ""
dfMCAR$group <- as.character(dfMCAR$group)
dfMCAR$group <- factor(dfMCAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMCAR <- ggplot(dfMCAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```

```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar1MAR[c(1,3,5,7,9),1],PercVar1MAR[c(1,3,5,7,9),2],PercVar1MAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar1MAR[c(2,4,6,8,10),1],PercVar1MAR[c(2,4,6,8,10),2],PercVar1MAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMAR<- data.frame(bias=rbind(t(MAR10Full[1,Var1Inds]),t(MAR30Full[1,Var1Inds]),t(MAR50Full[1,Var1Inds])),sd=rbind(t(MAR10Full[2,Var1Inds]),t(MAR30Full[2,Var1Inds]),t(MAR50Full[2,Var1Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMAR)
dfMAR <- cbind(dfMAR,feats)
dfMAR$feats <- factor(dfMAR$feats, levels = dfMAR$feats[order(dfMAR$prop)])

dfMAR <- dfMAR[-c(6,11),]
dfMAR$prop <- as.character(dfMAR$prop)
dfMAR[1,6]<- ""
dfMAR$group <- as.character(dfMAR$group)
dfMAR$group <- factor(dfMAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMAR <- ggplot(dfMAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```

```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar1MNAR1[c(1,3,5,7,9),1],PercVar1MNAR1[c(1,3,5,7,9),2],PercVar1MNAR1[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar1MNAR1[c(2,4,6,8,10),1],PercVar1MNAR1[c(2,4,6,8,10),2],PercVar1MNAR1[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10aFull[1,Var1Inds]),t(MNAR30aFull[1,Var1Inds]),t(MNAR50aFull[1,Var1Inds])),sd=rbind(t(MNAR10aFull[2,Var1Inds]),t(MNAR30aFull[2,Var1Inds]),t(MNAR50aFull[2,Var1Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR1 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```

```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar1MNAR2[c(1,3,5,7,9),1],PercVar1MNAR2[c(1,3,5,7,9),2],PercVar1MNAR2[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar1MNAR2[c(2,4,6,8,10),1],PercVar1MNAR2[c(2,4,6,8,10),2],PercVar1MNAR2[c(2,4,6,8,10),3]))
colnames(upper) <- c()



dfMNAR<- data.frame(bias=rbind(t(MNAR10bFull[1,Var1Inds]),t(MNAR30bFull[1,Var1Inds]),t(MNAR50bFull[1,Var1Inds])),sd=rbind(t(MNAR10bFull[2,Var1Inds]),t(MNAR30bFull[2,Var1Inds]),t(MNAR50bFull[2,Var1Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR2 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```

```{r,echo=F}
library (gridExtra)

plotMCAR = plotMCAR + ggtitle("MCAR")
plotMAR = plotMAR + ggtitle("MAR")
plotMNAR1 = plotMNAR1 + ggtitle("MNAR1")
plotMNAR2 = plotMNAR2 + ggtitle("MNAR2")
plotTxt = grid.arrange(plotMCAR, plotMAR, plotMNAR1, plotMNAR2, nrow = 2)
#plot (plotTxt)

png('~/Desktop/plotAllVar1.png', width=10, height=8, units="in", pointsize=2, res=300)
plot (plotTxt)
dev.off()

```



\newpage

# Var2 Percentiles of Est - Truth
```{r,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar2MCAR[c(1,3,5,7,9),1],PercVar2MCAR[c(1,3,5,7,9),2],PercVar2MCAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar2MCAR[c(2,4,6,8,10),1],PercVar2MCAR[c(2,4,6,8,10),2],PercVar2MCAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()

dfMCAR<- data.frame(bias=rbind(t(MCAR10Full[1,Var2Inds]),t(MCAR30Full[1,Var2Inds]),t(MCAR50Full[1,Var2Inds])),sd=rbind(t(MCAR10Full[2,Var2Inds]),t(MCAR30Full[2,Var2Inds]),t(MCAR50Full[2,Var2Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMCAR)
dfMCAR <- cbind(dfMCAR,feats)
dfMCAR$feats <- factor(dfMCAR$feats, levels = dfMCAR$feats[order(dfMCAR$prop)])

dfMCAR <- dfMCAR[-c(6,11),]
dfMCAR$prop <- as.character(dfMCAR$prop)
dfMCAR[1,6]<- ""
dfMCAR$group <- as.character(dfMCAR$group)
dfMCAR$group <- factor(dfMCAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMCAR <- ggplot(dfMCAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)


```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar2MAR[c(1,3,5,7,9),1],PercVar2MAR[c(1,3,5,7,9),2],PercVar2MAR[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar2MAR[c(2,4,6,8,10),1],PercVar2MAR[c(2,4,6,8,10),2],PercVar2MAR[c(2,4,6,8,10),3]))
colnames(upper) <- c()

dfMAR<- data.frame(bias=rbind(t(MAR10Full[1,Var2Inds]),t(MAR30Full[1,Var2Inds]),t(MAR50Full[1,Var2Inds])),sd=rbind(t(MAR10Full[2,Var2Inds]),t(MAR30Full[2,Var2Inds]),t(MAR50Full[2,Var2Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMAR)
dfMAR <- cbind(dfMAR,feats)
dfMAR$feats <- factor(dfMAR$feats, levels = dfMAR$feats[order(dfMAR$prop)])

dfMAR <- dfMAR[-c(6,11),]
dfMAR$prop <- as.character(dfMAR$prop)
dfMAR[1,6]<- ""
dfMAR$group <- as.character(dfMAR$group)
dfMAR$group <- factor(dfMAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMAR <- ggplot(dfMAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar2MNAR1[c(1,3,5,7,9),1],PercVar2MNAR1[c(1,3,5,7,9),2],PercVar2MNAR1[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar2MNAR1[c(2,4,6,8,10),1],PercVar2MNAR1[c(2,4,6,8,10),2],PercVar2MNAR1[c(2,4,6,8,10),3]))
colnames(upper) <- c()


dfMNAR<- data.frame(bias=rbind(t(MNAR10aFull[1,Var2Inds]),t(MNAR30aFull[1,Var2Inds]),t(MNAR50aFull[1,Var2Inds])),sd=rbind(t(MNAR10aFull[2,Var2Inds]),t(MNAR30aFull[2,Var2Inds]),t(MNAR50aFull[2,Var2Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR1 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{R,echo=F}
upperlim <- .03
lowerlim <- -.03

lower <- data.frame(c(PercVar2MNAR2[c(1,3,5,7,9),1],PercVar2MNAR2[c(1,3,5,7,9),2],PercVar2MNAR2[c(1,3,5,7,9),3]))
colnames(lower) <- c()
upper <- data.frame(c(PercVar2MNAR2[c(2,4,6,8,10),1],PercVar2MNAR2[c(2,4,6,8,10),2],PercVar2MNAR2[c(2,4,6,8,10),3]))
colnames(upper) <- c()


dfMNAR<- data.frame(bias=rbind(t(MNAR10bFull[1,Var2Inds]),t(MNAR30bFull[1,Var2Inds]),t(MNAR50bFull[1,Var2Inds])),sd=rbind(t(MNAR10bFull[2,Var2Inds]),t(MNAR30bFull[2,Var2Inds]),t(MNAR50bFull[2,Var2Inds])),lower,upper,group=rep(c("ORACLE","CC","MICE", "RF","DAE"),3),prop=c(rep("10%",5),rep("30%",5),rep("50%",5)))  
feats= rownames(dfMNAR)
dfMNAR <- cbind(dfMNAR,feats)
dfMNAR$feats <- factor(dfMNAR$feats, levels = dfMNAR$feats[order(dfMNAR$prop)])

dfMNAR <- dfMNAR[-c(6,11),]
dfMNAR$prop <- as.character(dfMNAR$prop)
dfMNAR[1,6]<- ""
dfMNAR$group <- as.character(dfMNAR$group)
dfMNAR$group <- factor(dfMNAR$group, levels=c("ORACLE", "CC", "MICE","RF","DAE"))

mycols = c ("#D55E00", "#E69F00", "#2271B2", "#3DB7E9", "#359B73")

plotMNAR2 <- ggplot(dfMNAR, aes(x = group,y=bias,color = group)) +
        ylab("Bias")+ xlab("")+
  geom_errorbar(aes(ymax =upper, ymin = lower),
                position = "dodge",size = 1.5)+ geom_hline(yintercept=0, linetype="dashed", color = "black")+geom_point(shape=16,colour="black",size=2)+   facet_grid(cols=vars(prop),scales = "free_x",space="free_x",switch="both") +theme(panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         axis.line = element_line(colour = "grey"),
         panel.grid.major.y =element_line(colour = "grey"),
         strip.placement = "outside",
         axis.text.x = element_text(angle = 45, hjust = 1,size=10),
         panel.background = element_rect(fill = 'white', colour = 'white'))+ scale_x_discrete(breaks=c("CC","MICE","RF","DAE","ORACLE"))+ theme(legend.position = 'none')+scale_color_manual(values=mycols)

```


```{r,echo=F}
library (gridExtra)

plotMCAR = plotMCAR + ggtitle("MCAR")
plotMAR = plotMAR + ggtitle("MAR")
plotMNAR1 = plotMNAR1 + ggtitle("MNAR1")
plotMNAR2 = plotMNAR2 + ggtitle("MNAR2")
plotTxt = grid.arrange(plotMCAR, plotMAR, plotMNAR1, plotMNAR2, nrow = 2)
#plot (plotTxt)

png('~/Desktop/plotAllVar2.png', width=10, height=8, units="in", pointsize=2, res=300)
plot (plotTxt)
dev.off()

```



















